Negative Types

### 2019-04-11 fractionals/p.tex
my thoughts on the ideas on fractional

>>>>

===============================================================

Comments on the above:

I am going to use a mixture of 'reversible', 'functional' and 'imperative' thinking below,
and may not always signal it explicitly -- you've been warned!

So a getter is 1 -> A only in an imperative setting. In a functional setting, the 'better' type
is World -> A; and a setter is then World -> A -> World. Which is great, because THAT is
actually exactly the type of a lens! [We could generalize to World' as the result of set,
which would push us into generalized optics]

The 'reasoning' to get to A and 1/A is dubious at best; it uses 'Boolean' Curry-Howard,
which is not reversible. I don't believe in that aspect at all.

However, I do see "Lens S A" as being a kind of 'relative complement', i.e. S // A.
And it does make complete sense to see World as being chopped-up, through allocation, into
A and its 'complement' World // A. Let's just call this 'Rest'.

Here World is some kind of 'potentially infinite' universe where a Lens does not
*necessarily* allocate new memory, but it certainly does reserve memory for our use.
Observationally, these are probably the same.

What do we obtain here? What seems to drop out quite naturally is a flavour of
separation logic!  The axioms of Lens, equivalently of isomorphisms and product, give
us exactly that!

Downside? World is _neither_ 1 or 0.  So 1 / A still doesn't pop out.
Nevertheless, I think this is very interesting.
